### 2016-11-15 ms_21cm.tex
latex template for RAA

\documentclass[]{raa}

\usepackage{aas_macros}
\usepackage{graphicx,times}
\usepackage{natbib}
\usepackage{amssymb,amsmath}
\bibpunct{(}{)}{;}{a}{}{,}

\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = green, anchorcolor = red, citecolor = blue, filecolor = red, pagecolor = red, urlcolor = red}

\newcommand{\cpm}{{\small CUBEP$^3$M}}
\newcommand{\smjustify}{\hspace{-0.1cm}}
\def\smwidth{0.48\textwidth}
\def\smhwidth{0.48\textwidth}

\begin{document}

\title{Searching 21-cm Absorption Systems in Chinese Radio Telescopes}

\author{
Hao-Ran Yu\inst{1,2},
Ue-Li Pen\inst{2,3,4,5},
Tong-Jie Zhang\inst{6},
Di Li\inst{7,8},
Xuelei Chen\inst{9}
}

\institute{
Kavli Institute for Astronomy \& Astrophysics, Peking University, Beijing 100871, China;\\ \and
Canadian Institute for Theoretical Astrophysics, University of Toronto, Toronto, M5S 3H8, ON, Canada;\\ \and
Dunlap Institute for Astronomy and Astrophysics, University of Toronto, Toronto, M5S 3H4, ON, Canada;\\ \and
Canadian Institute for Advanced Research, Program in Cosmology and Gravitation;\\ \and
Perimeter Institute for Theoretical Physics, Waterloo, ON, N2L 2Y5, Canada;\\ \and
Department of Astronomy, Beijing Normal University, Beijing, 100875, China;\\ \and
National Astronomical Observatories, Chinese Academy of Sciences, Beijing, China;\\ \and
Key Laboratory of Radio Astronomy, Chinese Academy of Sciences, Beijing, China;\\ \and
Key Laboratory for Computational Astrophysics, National Astronomical Observatories, Chinese Academy of Sciences, Beijing, 100012, China.\\
}

\abstract{
\keywords{}
}

\authorrunning{Yu et al.}
\titlerunning{Searching 21-cm absorption systems}

\maketitle

\section{Introduction}

\begin{acknowledgements}
HRY acknowledges General Financial Grant No.2015M570884 and
Special Financial Grant No. 2016T90009 from the China
Postdoctoral Science Foundation.
HRY and ULP acknowledge the support of the
National Science and Engineering Research Council of Canada.
\end{acknowledgements}

\bibliographystyle{raa}
\bibliography{haoran_ref}

\end{document}

### 2016-11-15 ms_21cm.tex
add refs

@@
 
+\newcommand{\diff}{{\rm d}}
 \newcommand{\cpm}{{\small CUBEP$^3$M}}
@@
 Tong-Jie Zhang\inst{6},
-Di Li\inst{7,8},
+Di Li\inst{7,8} and
 Xuelei Chen\inst{9}
@@
 
+FAST \citep{2016RaSc...51.1060L} and Tianlai \citep{2012IJMPS..12..256C}. Direct measurement of cosmic acceleration
+\citep{2012ApJ...761L..26D}, and its proposal
+on CHIME \citep{2014PhRvL.113d1303Y}
+
+Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
+
+NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
+
+Recent studies show that the number density of absorbers to be $\diff N/\diff z\sim 0.45$
+\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}.
+
+Recent discoveries of 21-cm absorption systems have about $20\%$ fractional depth
+\citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z}.
+
 \begin{acknowledgements}

### 2016-11-17 ms_21cm.tex
abstract

@@
 \abstract{
+Neutral hydrogen clouds are known to exist in the Universe, however their spatial
+distributions and physical properties are poorly understood. Such missing information
+can be studied by the Chinese new generation radio telescopes by a blind searching
+of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
+systems by two representative radio telescopes --
+Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
+Tianlai. The result shows that, in a few of years term,
+these telescopes with either high sensitivity (FAST)
+or wide field of view (Tianlai) can discover orders of magnitudes
+more 21-cm absorption systems, than the cumulative discoveries
+in the past 50 years. 
 \keywords{}
@@
 \section{Introduction}
+21-cm absorption systems can be used to directly measure the cosmic acceleration
+via Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
+The current best constraint of this acceleration if given by 
+\cite{2012ApJ...761L..26D}. A proposal
+on CHIME-like telescope is given by \cite{2014PhRvL.113d1303Y},
+in which the minor redshift drift could be measured over decades.
+The uncertainties are from the poorly understood neutral hydrogen
+clouds. Path finder surveys, taking less than a year, are needed
+to improve our understandings of spatial distribution and physical
+properties of neutral hydrogen clouds.
+This can be done by the Chinese new generation radio telescopes --
+Five-hundred-meter Aperture Spherical radio Telescope (FAST)
+\citep{2016RaSc...51.1060L} and
+Tianlai \citep{2012IJMPS..12..256C}.
 
-FAST \citep{2016RaSc...51.1060L} and Tianlai \citep{2012IJMPS..12..256C}. Direct measurement of cosmic acceleration
-\citep{2012ApJ...761L..26D}, and its proposal
-on CHIME \citep{2014PhRvL.113d1303Y}
-
-Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
+\section{Sensitivity}
 
@@
 \citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z}.
+
+\section{FAST estimation}
+
+Parameters:
+
+Result: 90 per month.
+
+\section{Tianlai estimation}
+
+Parameters:
+
+Result: 80 per year.
+
+\section{Conclusion}
 

### 2016-11-18 ms_21cm.tex
introduction

@@
 \newcommand{\smjustify}{\hspace{-0.1cm}}
+\newcommand{\HI}{{H{\small\,I}}}
 \def\smwidth{0.48\textwidth}
@@
 of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
-systems by two representative radio telescopes --
+systems by two representative radio telescopes in China --
 Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
@@
 
-\section{Introduction}
-21-cm absorption systems can be used to directly measure the cosmic acceleration
-via Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
-The current best constraint of this acceleration if given by 
-\cite{2012ApJ...761L..26D}. A proposal
-on CHIME-like telescope is given by \cite{2014PhRvL.113d1303Y},
-in which the minor redshift drift could be measured over decades.
+\section{Introduction}\label{sec.introduction}
+Neutral hydrogen (\HI) clouds are known to exist in the Universe,
+however only few of them are discovered in the past half a century,
+and we poorly understand their spatial distribution and physical
+properties \citep{2005ARA&A..43..861W}. 
+In damped Lyman-$\alpha$ absorption (DLA)
+systems, the radio spectrum is also substantially absorbed by the {\HI}
+hyperfine structure, whose rest frame wavelength is approximately 21 cm
+($\sim$1420 MHz in frequency). These systems are defined to have
+at least $2\times 10^{20}$ cm$^{-2}$ {\HI} column density, thus being
+able to house cold 21-cm absorbing gas in the cold neutral medium (CNM).
+
+The 21-cm absorption systems are important in the study of the 
+distribution, location, temperature and structure of neutral gas,
+and the evolution of neutral gas systems and galaxies over
+cosmic time scale.
+Due to the narrow intrinsic line width, the 21-cm absorption systems
+are proposed to be used to directly measure the cosmic acceleration
+\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
+Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
 The uncertainties are from the poorly understood neutral hydrogen
@@
 \citep{2016RaSc...51.1060L} and
-Tianlai \citep{2012IJMPS..12..256C}.
+Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
+these are the two symbolic modern radio telescopes in China.
+The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
+uses its gigantic single dish to achieve ultimate sensitivity, whereas
+Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
+has ultra wide field of view per day, by
+using its cylindrical reflectors and arrays of receivers to
+scan the northern hemisphere of the sky as the Earth turns.
 
-\section{Sensitivity}
+According to their different design and observing strategies,
+we forecast their abilities of blind searching of 21-cm absorption
+systems. In section \ref{sec.sensitivity} we show the sensitivity
+estimation and all the aspects
+needed to be taken into account,
+and according to the configurations of FAST and Tianlai,
+we show their forecast in section \ref{sec.FAST}
+and section \ref{sec.Tianlai} respectively.
+Conclusions are made in section \ref{sec.conclusion}.
+
+\section{Sensitivity}\label{sec.sensitivity}
 
@@
 
-\section{FAST estimation}
+\section{FAST estimation}\label{sec.FAST}
 
@@
 
-\section{Tianlai estimation}
+\section{Tianlai estimation}\label{sec.Tianlai}
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec.conclusion}
 

### 2016-11-19 ms_21cm.tex
sensitivity section

@@
 Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
-has ultra wide field of view per day, by
+has ultra wide field of view (FoV) per day, by
 using its cylindrical reflectors and arrays of receivers to
@@
 \section{Sensitivity}\label{sec.sensitivity}
+To find possible 21-cm absorption systems, radio telescopes
+could be devised to scan the radio sources in
+NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
+If we assume the distributions of radio sources $n_R$ and
+{\HI} clouds $n_{\rm \HI}$ are uniform over the sky, then the redshift
+distribution of the 21-cm absorption systems $n_{\rm system}$ would be
+\begin{equation}
+    n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
+\end{equation}
+regardless of the observation sensitivity,
+where $n_R(z)$ is given by equation (26) of \cite{2010A&ARv..18....1D}.
+Spacial distribution of {\HI} is poorly understood and is to be
+studied in upcoming surveys.
+Recent studies show that the number density of
+absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
+per line of sight
+\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
+in the following forcast.
 
-NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
+Observation sensitivity depends on the background fluxes and foreground
+absorptions (current section), as well as telescope configurations and
+observation strategies (section \ref{sec.FAST},\ref{sec.Tianlai}).
 
-Recent studies show that the number density of absorbers to be $\diff N/\diff z\sim 0.45$
-\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}.
+NVSS contains 2 million sources (with declination $\delta >-40^{\circ}$,
+cover 82\% of the sky) stronger than 2.5
+mJy at $\nu=$1.4 GHz \citep{1998AJ....115.1693C} and their flux
+distribution $n_R(F)$ is given by \cite{1984ApJ...287..461C}.
+Redshifted {\HI} clouds absorb lower frequency bands where
+the radio sources are typically brighter by $\nu^{-0.7}$
+\citep{1998AJ....115.1693C}, or $(1+z_{\rm \HI})^{0.7}$.
+The error of the measurement $\Delta F$ is given by
+\begin{equation}
+    \Delta F={\rm SEFD}/\sqrt{n_{\rm pol}\Delta\nu\Delta t},
+\end{equation}
+where SEFD is the system equivalent flux density, $n_{\rm pol}$
+is the number of polarizations, $\Delta\nu$ is the line width and
+$\Delta t$ is the integration time. $\Delta\nu=(u_{\rm width}/c)\nu_{\rm obs}$,
+where $u_{\rm width}$ is the equivalent line width of the {\HI}
+absorber. The properties of 21-cm absorbers are primarily derived from
+followup studies of optical absorbers. The discovery rate from the
+cross correlation is a lower bound on the expect number of absorbers,
+since high column density systems in the CNM may systematically
+obscure potential background optical sources \citep{2014PhRvL.113d1303Y}. There are
+only 3 blind radio detections, and a survey may discover more systems
+which are optically obscured. They would likely be cold and at high
+column density. For sensitivity purposes, we treat all sources as
+$u_{\rm width}=2\ {\rm km\ s}^{-1}$
+\citep{1982ApJ...259..495W,2005ARA&A..43..861W}.
+$\nu_{\rm obs}$ is the observation frequency. For redshifted
+21-cm absorption systems, $\nu_{\rm obs}=1420\ {\rm MHz}/(1+z_{\rm \HI})$.
+The integration time $\Delta t=(n_{\rm obs}\times 24\ {\rm h})\tau$,
+where $n_{\rm obs}$ is the number of days an object is scanned,
+and $\tau=\lambda/2\pi D\cos\delta$ is the fractional time the object
+transits the FoV ($\lambda_{\rm obs}\ll D$ or $\delta\nrightarrow\pi/2$).
+For 21-cm absorption systems $\lambda_{\rm obs}=21\ {\rm cm}\times (1+z_{\rm obs})$.
 
-Recent discoveries of 21-cm absorption systems have about $20\%$ fractional depth
-\citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z}.
+In the forecast we count $>10\sigma$ detections, i.e., the absorption
+line depth is at least $10\Delta F$. The optical depth of {\HI} absorbers
+are also poorly understood. Recent discoveries of 21-cm absorption systems
+have about $r=20\%$ fractional depth \citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z},
+and we apply this value. Thus, all systems with $rF>10\Delta F$ are counted.
 
@@
 Parameters:
+
+Different declinations have different SEFD.
 

### 2016-11-20 ms_21cm.tex
section FAST

@@
 distribution of the 21-cm absorption systems $n_{\rm system}$ would be
-\begin{equation}
+\begin{equation}\label{eq.n_system}
     n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
@@
 
-NVSS contains 2 million sources (with declination $\delta >-40^{\circ}$,
+NVSS contains 2 million sources (with declination $\delta >-40^\circ$,
 cover 82\% of the sky) stronger than 2.5
@@
 The error of the measurement $\Delta F$ is given by
-\begin{equation}
+\begin{equation}\label{eq.delta_F}
     \Delta F={\rm SEFD}/\sqrt{n_{\rm pol}\Delta\nu\Delta t},
@@
 where $n_{\rm obs}$ is the number of days an object is scanned,
-and $\tau=\lambda/2\pi D\cos\delta$ is the fractional time the object
+and $\tau=\lambda_{\rm obs}/2\pi D\cos\delta$ is the fractional time the object
 transits the FoV ($\lambda_{\rm obs}\ll D$ or $\delta\nrightarrow\pi/2$).
 For 21-cm absorption systems $\lambda_{\rm obs}=21\ {\rm cm}\times (1+z_{\rm obs})$.
+$\Delta F$ is redshift- (frequency-) independent, as $(1+z_{\rm obs})$ terms
+from integration time and line width cancel out
+in the equation (\ref{eq.delta_F}).
 
@@
 
-Parameters:
+FAST has a fixed 500 m dish, and a circle of 300 m diameter is held
+in the correct parabolic shape, being used at any one time. This
+enables its zenith angle to be $40^\circ$ and it can scan objects
+in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
+The 19-beam feed-horn array at L band will be the primary survey
+instrument for FAST. For a single day it can scan $0.762^\circ$
+in declination $\delta$. FAST survey strategy scans each object
+only once ($n_{\rm obs}=1$), and with its high sensitivity,
+even faint sources are identified in a single day. 
+We assume a one-month survey by FAST
+around the celestial equator for simplicity. FAST observes
+1.2 to 1.4 GHz (redshift $z_{\rm \HI}<0.2$), so objects on celestial equator
+have average transit time $\Delta t \simeq 10\ {\rm sec.}$
+Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$, and
+${\rm SEFD}=1$ Jy for FAST.
+we have $\Delta F \simeq\ 2.3 {\rm mJy}$.
+Taking into account the $\nu^{-0.7}$ flux boost at lower
+frequencies, $rF>10\Delta F$ requires $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.
 
-Result: 90 per month.
+One-month-scan ($n_{\rm obs}=30$) around celestial equator by FAST will have
+$N_R\simeq 10^4$ sources whose $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.
+We further assume the independency between $n_R(F)$, $n_R(z)$
+and $n_{\rm\HI}(z)$, from $n_{\rm system}(z)$ by integrating
+equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90$ absorption
+systems found in redshift range $0<z<0.2$.
 
@@
 
-Parameters:
+Tianlai is currently $30\times 12 {\rm m}$ area with
+${\rm SEFD}\simeq 300\ {\rm Jy}$. Different from FAST, however,
+Tianlai scans all sources in the northern hemisphere of the sky
+everyday, and one needs longer periods integration to
+identify absorbers with fainter background sources.
+We forecast its one-year-survey ability of searching 21-cm
+absorption systems in the northern hemisphere.
+
+Because Tianlai locates at latitude
+$\phi_{\rm site}=+44^\circ$ and its cylinders are fixed, only
+objects at the zenith ($\delta=\phi_{\rm cite}=44^\circ$) fully utilize
+the SEFD. On the other hand, higher declination objects
+have longer integration time per day. Thus, $\Delta F$ is
+a function of $\delta$.
 

### 2016-11-20 ms_21cm.tex
section Tianlai

@@
 \authorrunning{Yu et al.}
-\titlerunning{Searching 21-cm absorption systems}
+\titlerunning{Searching 21-cm Absorption Systems}
 
@@
 and $n_{\rm\HI}(z)$, from $n_{\rm system}(z)$ by integrating
-equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90$ absorption
+equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90 {\rm /month}$ absorption
 systems found in redshift range $0<z<0.2$.
@@
 
-Tianlai is currently $30\times 12 {\rm m}$ area with
+Tianlai is currently $30\times 12\ {\rm m}$ area with
 ${\rm SEFD}\simeq 300\ {\rm Jy}$. Different from FAST, however,
@@
 have longer integration time per day. Thus, $\Delta F$ is
-a function of $\delta$.
-
-Different declinations have different SEFD.
-
-Result: 80 per year.
+a function of $\delta$, 
+\begin{equation}\label{eq.delta_F_delta}
+    \Delta F(\delta) = \frac{\rm SEFD}{\cos(\delta-\phi_{\rm site})}
+    {\sqrt{\frac{\cos\delta}{n_{\rm pol}\Delta\nu\Delta t(\delta=0)}}},
+\end{equation}
+where $\Delta t(\delta=0)\simeq 1.17\times 10^5\ {\rm sec}$ is the
+total integration time (1-year survey) for objects on celestial equator,
+for Tianlai frequency range 800 to 900 MHz ($0.58<z<0.78$).
+The effective $N_R$ is given by
+\begin{equation}\label{eq.N_R_eff}
+    N_R=\int_0^{\pi/2}2\pi\cos\delta
+    \left(\int_{10\Delta F(\delta)/r}^{+\infty}
+    n_R(F')\diff F'\right)
+    \diff\delta.
+\end{equation}
+Note that the inner flux integration converges as
+$F'\rightarrow+\infty$ because $n_R(F)\sim F^{-2.5}$.
+Additionally, even if $\tau=\lambda_{\rm obs}/2\pi D\cos\delta$
+fails at $\delta\rightarrow\pi/2$ (the north pole
+$\tau(\delta=\pi/2)=1$ is always in FoV),
+the outer declination integration also converges
+as $\delta\rightarrow\pi/2$, because the pole area is
+tiny and neglectable.
+Equation (\ref{eq.N_R_eff}) gives $N_R\simeq 1.3\times 10^4$,
+and applying it to equation (\ref{eq.n_system}) again
+we get $N_{\rm system}\simeq 80 {\rm /year}$ absorption
+systems found in redshift range $0.58<z<0.78$.
 

### 2016-11-20 ms_21cm.tex
conclusion

@@
 tiny and neglectable.
-Equation (\ref{eq.N_R_eff}) gives $N_R\simeq 1.3\times 10^4$,
+For FAST, surveys at higher declinations would as well
+use equation (\ref{eq.delta_F_delta},\ref{eq.N_R_eff}),
+however $\cos(\delta-\phi_{\rm site})$ term affecting
+SEFD should be neglected.
+
+For Tianlai, equation (\ref{eq.N_R_eff}) gives $N_R\simeq 1.3\times 10^4$,
 and applying it to equation (\ref{eq.n_system}) again
@@
 \section{Conclusion}\label{sec.conclusion}
+We forecast the ability of FAST and Tianlai telescopes to search 21-cm
+absorption systems. According to our assumptions, FAST is able
+to find $\simeq 90$ systems per month
+whereas TianLai can find $\simeq 80$ systems per year.
+Comparing the results between two quite different telescopes --
+high sensitivity FAST and large FoV Tianlai, we find the former is
+more efficient in looking for fainter radio sources
+($n_R(F)\sim F^{-2.5}$) for possible foreground absorptions.
+Future improvements in the sensitivity on Tianlai enable it
+more effectively looking for highest signal-to-noise systems
+over a wider sky.
+
+Regarding the quantitative forecasts in each telescope, although we take
+into account many detailed aspects affecting the result, the major
+uncertainties are $n_{\rm \HI}(z)$, $u_{\rm width}$ and $r$.
+These poorly understood parameters are conversely worth investigating
+from these proposed surveys. Modest real-time analysis changes could
+allow the survey of 21-cm absorption systems. The data would need to be
+recorded at sufficient spectral resolution. Spatial computational costs are
+in principle unchanged, but there could be additional overhead
+costs for the larger resulting data sets.
 

### 2016-11-22 ms_21cm.tex
title, science goal

@@
 
-\title{Searching 21-cm Absorption Systems in Chinese Radio Telescopes}
+\title{Blind Search for 21-cm Absorption Systems in New Generation Chinese Radio Telescopes}
 
@@
 distributions and physical properties are poorly understood. Such missing information
-can be studied by the Chinese new generation radio telescopes by a blind searching
+can be studied by the new generation Chinese radio telescopes by a blind searching
 of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
@@
 Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
-Tianlai. The result shows that, in a few of years term,
+Tianlai 21-cm cosmology experiment (Tianlai).
+The result shows that, in a few of years term,
 these telescopes with either high sensitivity (FAST)
@@
 \authorrunning{Yu et al.}
-\titlerunning{Searching 21-cm Absorption Systems}
+\titlerunning{Blind Search for 21-cm Absorption Systems}
 
@@
 Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
-The uncertainties are from the poorly understood neutral hydrogen
-clouds. Path finder surveys, taking less than a year, are needed
+The uncertainties of these decade-long proposals are from the poorly understood
+{\HI} clouds \citep{2014PhRvL.113d1303Y}.
+Path finder surveys, taking less than a year, are able
 to improve our understandings of spatial distribution and physical
-properties of neutral hydrogen clouds.
+properties of {\HI} clouds.
 This can be done by the Chinese new generation radio telescopes --
 Five-hundred-meter Aperture Spherical radio Telescope (FAST)
-\citep{2016RaSc...51.1060L} and
-Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
-these are the two symbolic modern radio telescopes in China.
+\citep{2016RaSc...51.1060L} and Tianlai 21-cm cosmology experiment
+(Tianlai) \citep{2012IJMPS..12..256C}. In the current and near future,
+these are the two symbolic new generation radio telescopes in China.
 The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
@@
 systems. In section \ref{sec.sensitivity} we show the sensitivity
-estimation and all the aspects
-needed to be taken into account,
+estimation and related factors needed taken into account,
 and according to the configurations of FAST and Tianlai,
@@
 absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
-per line of sight
+per line of sight at low and medium redshift
 \citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
 in the following forcast.
-
 Observation sensitivity depends on the background fluxes and foreground
@@
 
-FAST has a fixed 500 m dish, and a circle of 300 m diameter is held
+FAST has a fixed 500-meter-dish, and a circle of 300 meter in diameter is held
 in the correct parabolic shape, being used at any one time. This
-enables its zenith angle to be $40^\circ$ and it can scan objects
+enables its zenith angle up to $40^\circ$ and it can scan objects
 in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
 The 19-beam feed-horn array at L band will be the primary survey
-instrument for FAST. For a single day it can scan $0.762^\circ$
+instrument for FAST. For a single day it can scan total of $0.762^\circ$
 in declination $\delta$. FAST survey strategy scans each object
@@
 have average transit time $\Delta t \simeq 10\ {\rm sec.}$
-Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$, and
+Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$
+(dual polarized system), and
 ${\rm SEFD}=1$ Jy for FAST.
@@
 in principle unchanged, but there could be additional overhead
-costs for the larger resulting data sets.
+costs for the larger resulting data sets. Systematic surveys of
+{\HI} clouds over a cosmic scale enable us to measure the 3D density
+of these systems. For objects detected by FAST, one can also try to measure
+the 21cm emission size. For Tianlai, one can try to measure the size from
+very-long-baseline interferometry (VLBI).
 

### 2016-12-19 ms_21cm.tex
Di's modification

@@
 \usepackage{aas_macros}
-\usepackage{graphicx,times}
+\usepackage{graphicx,times,color}
 \usepackage{natbib}
@@
 \newcommand{\HI}{{H{\small\,I}}}
+\newcommand{\tcb}{\textcolor{blue}}
+\newcommand{\tcr}{\textcolor{red}}
 \def\smwidth{0.48\textwidth}
@@
 distributions and physical properties are poorly understood. Such missing information
-can be studied by the new generation Chinese radio telescopes by a blind searching
-of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
+can be studied by the new generation Chinese radio telescopes through a blind searching
+of 21-cm absorption systems. We forecast the capabilities of surveys of 21-cm absorption
 systems by two representative radio telescopes in China --
@@
 Tianlai 21-cm cosmology experiment (Tianlai).
-The result shows that, in a few of years term,
-these telescopes with either high sensitivity (FAST)
-or wide field of view (Tianlai) can discover orders of magnitudes
-more 21-cm absorption systems, than the cumulative discoveries
-in the past 50 years. 
+Facilitated by either the high sensitivity (FAST)
+or the wide field of view (Tianlai) of these telescopes,
+\tcr{???} 21-cm absorption systems can be discovered in a few years,
+representing orders of magnitude improvement over the cumulative discoveries
+in the past half a century. 
 \keywords{}
@@
 Neutral hydrogen (\HI) clouds are known to exist in the Universe,
-however only few of them are discovered in the past half a century,
+however relatively few of them are discovered in the past half a century,
 and we poorly understand their spatial distribution and physical
@@
 hyperfine structure, whose rest frame wavelength is approximately 21 cm
-($\sim$1420 MHz in frequency). These systems are defined to have
+($1420405751.7667\pm 0.009$ Hz in frequency). These systems have
 at least $2\times 10^{20}$ cm$^{-2}$ {\HI} column density, thus being
-able to house cold 21-cm absorbing gas in the cold neutral medium (CNM).
+able to absorb the background with its cold {\HI} in their cold neutral medium (CNM).
 
@@
 Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
-The uncertainties of these decade-long proposals are from the poorly understood
-{\HI} clouds \citep{2014PhRvL.113d1303Y}.
-Path finder surveys, taking less than a year, are able
+The main source of uncertainty of such proposed measurements lies in our
+poor understandings of {\HI} clouds \citep{2014PhRvL.113d1303Y}.
+New surveys are required
 to improve our understandings of spatial distribution and physical
@@
 \citep{2016RaSc...51.1060L} and Tianlai 21-cm cosmology experiment
-(Tianlai) \citep{2012IJMPS..12..256C}. In the current and near future,
-these are the two symbolic new generation radio telescopes in China.
+(Tianlai) \citep{2012IJMPS..12..256C}.
 The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
@@
 Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
-has ultra wide field of view (FoV) per day, by
+has ultra wide field of view (FoV) provided by its
 using its cylindrical reflectors and arrays of receivers to
-scan the northern hemisphere of the sky as the Earth turns.
+quickly scan the northern hemisphere of the sky as the Earth rotates.
 
-According to their different design and observing strategies,
-we forecast their abilities of blind searching of 21-cm absorption
+Considering their respective design and observing strategies,
+we forecast their capabilities of blind searching of 21-cm absorption
 systems. In section \ref{sec.sensitivity} we show the sensitivity
-estimation and related factors needed taken into account,
-and according to the configurations of FAST and Tianlai,
-we show their forecast in section \ref{sec.FAST}
+estimation and related factors for FAST and Tianlai.
+We present our forecast in section \ref{sec.FAST}
 and section \ref{sec.Tianlai} respectively.
@@
 If we assume the distributions of radio sources $n_R$ and
-{\HI} clouds $n_{\rm \HI}$ are uniform over the sky, then the redshift
+{\HI} clouds $n_{\rm \HI}$ are uncorrelated, the redshift
 distribution of the 21-cm absorption systems $n_{\rm system}$ would be
+\tcr{(still need a volume filling factor $K(z)$?)}
 \begin{equation}\label{eq.n_system}
-    n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
+    n_{\rm system}(z)=\tcr{n_{\rm \HI}(z)}\int_z^\infty n_R(z')\diff z'
 \end{equation}
+\tcr{(In my definition,
+$n_{\rm \HI}$ is the cloud regardless observable or not, 
+and $n_{\rm system}$ is the absorber, associated with a background source, absorbing the
+source flux on the line of sight to Earth.)}
 regardless of the observation sensitivity,
@@
 Recent studies show that the number density of
-absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
+absorbers to be $\diff \tcr{n_{\rm \HI}}/\diff z= 0.045\pm0.006$
 per line of sight at low and medium redshift
@@
 \citep{1998AJ....115.1693C}, or $(1+z_{\rm \HI})^{0.7}$.
-The error of the measurement $\Delta F$ is given by
+The error of the measurement $\Delta F$ is given by \tcr{[reference]}
 \begin{equation}\label{eq.delta_F}
@@
 \end{equation}
-where SEFD is the system equivalent flux density, $n_{\rm pol}$
+where SEFD \tcr{(or $T_{\rm sys}$ TBD)} is the system equivalent flux density, $n_{\rm pol}$
 is the number of polarizations, $\Delta\nu$ is the line width and
@@
 identify absorbers with fainter background sources.
-We forecast its one-year-survey ability of searching 21-cm
+We forecast its one-year-survey capability of searching 21-cm
 absorption systems in the northern hemisphere.
@@
 \section{Conclusion}\label{sec.conclusion}
-We forecast the ability of FAST and Tianlai telescopes to search 21-cm
+We forecast the capability of FAST and Tianlai telescopes to search 21-cm
 absorption systems. According to our assumptions, FAST is able

### 2016-12-23 ms_21cm.tex
update numbers

@@
 or the wide field of view (Tianlai) of these telescopes,
-\tcr{???} 21-cm absorption systems can be discovered in a few years,
+\tcr{??? [more than a thousand for FAST]} 21-cm absorption systems can be discovered in a few years,
 representing orders of magnitude improvement over the cumulative discoveries
@@
 \citep{1998AJ....115.1693C}, or $(1+z_{\rm \HI})^{0.7}$.
-The error of the measurement $\Delta F$ is given by \tcr{[reference]}
+The error of the measurement $\Delta F$ is given by\footnote{https://science.nrao.edu/facilities/vla/docs/manuals/oss/performance/sensitivity} \tcr{[confirm this reference]}
 \begin{equation}\label{eq.delta_F}
@@
 
-FAST has a fixed 500-meter-dish, and a circle of 300 meter in diameter is held
-in the correct parabolic shape, being used at any one time. This
-enables its zenith angle up to $40^\circ$ and it can scan objects
-in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
+FAST has a primary dish of 500 meter in diameter. The effective
+antenna aperture of FAST is 300 m, in diameter for any zenith angle
+up to $26^\circ$ and decreases to 200 m for a maximum zenith angle 
+of $40^\circ$ \citep{2016RaSc...51.1060L}.
+%This enables its zenith angle up to $40^\circ$ and it can scan objects
+%in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
 The 19-beam feed-horn array at L band will be the primary survey
-instrument for FAST. For a single day it can scan total of $0.762^\circ$
+instrument for FAST. For a single day it can scan total of \tcr{$0.5^\circ$ (TBD)}
 in declination $\delta$. FAST survey strategy scans each object
@@
 around the celestial equator for simplicity. FAST observes
-1.2 to 1.4 GHz (redshift $z_{\rm \HI}<0.2$), so objects on celestial equator
-have average transit time $\Delta t \simeq 10\ {\rm sec.}$
+1.02 to 1.42 GHz (redshift $z_{\rm \HI}<0.39$), so objects on celestial equator
+have average transit time $\Delta t \simeq \tcr{12}\ {\rm sec.}$
 Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$
@@
 ${\rm SEFD}=1$ Jy for FAST.
-we have $\Delta F \simeq\ 2.3 {\rm mJy}$.
+we have $\Delta F \simeq\ 2.3\ {\rm mJy}$.
 Taking into account the $\nu^{-0.7}$ flux boost at lower
@@
 and $n_{\rm\HI}(z)$, from $n_{\rm system}(z)$ by integrating
-equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90 {\rm /month}$ absorption
-systems found in redshift range $0<z<0.2$.
+equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq \tcr{210} {\rm /month}$ absorption
+systems found in redshift range $0<z<0.39$.
 
@@
 and applying it to equation (\ref{eq.n_system}) again
-we get $N_{\rm system}\simeq 80 {\rm /year}$ absorption
+we get $N_{\rm system}\simeq \tcr{80} {\rm /year}$ absorption
 systems found in redshift range $0.58<z<0.78$.
@@
 absorption systems. According to our assumptions, FAST is able
-to find $\simeq 90$ systems per month
+to find $\simeq 210$ systems per month
 whereas TianLai can find $\simeq 80$ systems per year.

### 2017-01-13 ms_21cm.tex
SEFD -> T_sys; confusion limit

@@
 or the wide field of view (Tianlai) of these telescopes,
-\tcr{??? [more than a thousand for FAST]} 21-cm absorption systems can be discovered in a few years,
+\tcr{[more than a thousand for FAST (and Tianlai)] (to be determined by final calculations)} 21-cm absorption systems can be discovered in a few years,
 representing orders of magnitude improvement over the cumulative discoveries
@@
 \begin{equation}\label{eq.delta_F}
-    \Delta F={\rm SEFD}/\sqrt{n_{\rm pol}\Delta\nu\Delta t},
+    \tcr{\Delta F=T_{\rm sys}A_{\rm eff}^{-1}/\sqrt{n_{\rm pol}\Delta\nu\Delta t}},
 \end{equation}
-where SEFD \tcr{(or $T_{\rm sys}$ TBD)} is the system equivalent flux density, $n_{\rm pol}$
+where
+\tcr{$T_{\rm sys}$ and $A_{\rm eff}$ are system temperature and effective receiving area,}
+%SEFD \tcr{(or $T_{\rm sys}$ TBD)} is the system equivalent flux density,
+$n_{\rm pol}$
 is the number of polarizations, $\Delta\nu$ is the line width and
@@
 and we apply this value. Thus, all systems with $rF>10\Delta F$ are counted.
+\tcr{Note that there is no confusion in the spectral domain -- 
+When the system temperature is not dominated by sources,
+the noise in each pixel is not affected by the number of sources.
+So only sources with absorbers contribute to the signal, 
+and nothing contributes to the noise.
+Thus being confusion limited makes no difference.}
 
@@
 have average transit time $\Delta t \simeq \tcr{12}\ {\rm sec.}$
-Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$
-(dual polarized system), and
-${\rm SEFD}=1$ Jy for FAST.
+Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$ (dual polarized system),
+\tcr{$T_{\rm sys}\sim 20$ K and $A_{\rm eff}\sim 7\times 10^4$ m$^2$,
+(how do we get ${\rm SEFD}=1$ Jy for FAST???? In Li \& Pan (2016), I'm also
+confused how to get $A/T=2000$ m/K from these knwon numbers.)},
 we have $\Delta F \simeq\ 2.3\ {\rm mJy}$.
@@
 Tianlai is currently $30\times 12\ {\rm m}$ area with
-${\rm SEFD}\simeq 300\ {\rm Jy}$. Different from FAST, however,
+\tcr{${\rm SEFD}=T_{\rm sys}A_{\rm eff}^{-1}\simeq 300\ {\rm Jy}$}. Different from FAST, however,
 Tianlai scans all sources in the northern hemisphere of the sky
@@
 objects at the zenith ($\delta=\phi_{\rm cite}=44^\circ$) fully utilize
-the SEFD. On the other hand, higher declination objects
+$A_{\rm eff}$. On the other hand, higher declination objects
 have longer integration time per day. Thus, $\Delta F$ is
@@
 \begin{equation}\label{eq.delta_F_delta}
-    \Delta F(\delta) = \frac{\rm SEFD}{\cos(\delta-\phi_{\rm site})}
+    \Delta F(\delta) = \frac{\tcr{T_{\rm sys}A_{\rm eff}^{-1}}}{\cos(\delta-\phi_{\rm site})}
     {\sqrt{\frac{\cos\delta}{n_{\rm pol}\Delta\nu\Delta t(\delta=0)}}},

### 2017-03-15 ms_21cm.tex
v3

@@
 or the wide field of view (Tianlai) of these telescopes,
-\tcr{[more than a thousand for FAST (and Tianlai)] (to be determined by final calculations)} 21-cm absorption systems can be discovered in a few years,
+more than a thousand 21-cm absorption systems can be discovered in a few years,
 representing orders of magnitude improvement over the cumulative discoveries
@@
 NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
-If we assume the distributions of radio sources $n_R$ and
-{\HI} clouds $n_{\rm \HI}$ are uncorrelated, the redshift
+\tcr{If we assume the distributions of radio sources and
+{\HI} clouds are uncorrelated over the sky}, the redshift
 distribution of the 21-cm absorption systems $n_{\rm system}$ would be
-\tcr{(still need a volume filling factor $K(z)$?)}
 \begin{equation}\label{eq.n_system}
-    n_{\rm system}(z)=\tcr{n_{\rm \HI}(z)}\int_z^\infty n_R(z')\diff z'
+    n_{\rm system}(z)=n_{\rm \HI}^*(z)\int_z^\infty n_R(z')\diff z',
 \end{equation}
-\tcr{(In my definition,
-$n_{\rm \HI}$ is the cloud regardless observable or not, 
-and $n_{\rm system}$ is the absorber, associated with a background source, absorbing the
-source flux on the line of sight to Earth.)}
-regardless of the observation sensitivity,
-where $n_R(z)$ is given by equation (26) of \cite{2010A&ARv..18....1D}.
-Spacial distribution of {\HI} is poorly understood and is to be
-studied in upcoming surveys.
-Recent studies show that the number density of
-absorbers to be $\diff \tcr{n_{\rm \HI}}/\diff z= 0.045\pm0.006$
+\tcr{where $n_R$ is the redshift distribution of radio sources over the sky
+(given by equation (26) of \cite{2010A&ARv..18....1D}), and
+$n_{\rm \HI}^*(z)$ is the number of occupation of {\HI} clouds
+per any given line of sight. Note that, unlike $n_R$ and $n_{\rm system}$,
+ $n_{\rm \HI}^*(z)$ is not an
+integration of volume so we do not need a volume filling factor in
+equation \ref{eq.n_system}.}
+However, this spacial distribution of {\HI} is poorly understood and is to be
+studied in upcoming surveys. Recent studies show that the number density of
+absorbers to be $\diff n_{\rm \HI}/\diff z=n_{\rm \HI}^*(z)= 0.045\pm0.006$
 per line of sight at low and medium redshift
 \citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
-in the following forcast.
+in the following forcast. \tcr{Equation \ref{eq.n_system} gives the
+{\HI} cloud occupation regardless of observabilty, based on which
+we calculate the detections considering sensitivities.}
+
 Observation sensitivity depends on the background fluxes and foreground
@@
 distribution $n_R(F)$ is given by \cite{1984ApJ...287..461C}.
+\tcr{The observed flux is already lowered by the 21cm absorption if there is any on
+the line of sight, so the actual signal to noise of the absorption line
+is higher. Due to the limited knowledge of absorption system properties
+we ignore this factor for now.}
 Redshifted {\HI} clouds absorb lower frequency bands where
@@
 \citep{1998AJ....115.1693C}, or $(1+z_{\rm \HI})^{0.7}$.
-The error of the measurement $\Delta F$ is given by\footnote{https://science.nrao.edu/facilities/vla/docs/manuals/oss/performance/sensitivity} \tcr{[confirm this reference]}
+The error of the measurement $\Delta F$ is given by\footnote{https://science.nrao.edu/facilities/vla/docs/manuals/oss/performance/sensitivity}
 \begin{equation}\label{eq.delta_F}
-    \tcr{\Delta F=T_{\rm sys}A_{\rm eff}^{-1}/\sqrt{n_{\rm pol}\Delta\nu\Delta t}},
+    \Delta F=T_{\rm sys}A_{\rm eff}^{-1}/\sqrt{n_{\rm pol}\Delta\nu\Delta t},
 \end{equation}
 where
-\tcr{$T_{\rm sys}$ and $A_{\rm eff}$ are system temperature and effective receiving area,}
+\tcr{$T_{\rm sys}$ and $A_{\rm eff}$ are system temperature and effective receiving area,
+and $T_{\rm sys}A_{\rm eff}^{-1}$ is just the system equivalent flux density (SEFD).}
 %SEFD \tcr{(or $T_{\rm sys}$ TBD)} is the system equivalent flux density,
@@
 The 19-beam feed-horn array at L band will be the primary survey
-instrument for FAST. For a single day it can scan total of \tcr{$0.5^\circ$ (TBD)}
+instrument for FAST. For a single day it can scan total of $0.5^\circ$
 in declination $\delta$. FAST survey strategy scans each object
@@
 \tcr{$T_{\rm sys}\sim 20$ K and $A_{\rm eff}\sim 7\times 10^4$ m$^2$,
-(how do we get ${\rm SEFD}=1$ Jy for FAST???? In Li \& Pan (2016), I'm also
-confused how to get $A/T=2000$ m/K from these knwon numbers.)},
-we have $\Delta F \simeq\ 2.3\ {\rm mJy}$.
+we get ${\rm SEFD}\sim 1$ Jy for FAST},
+then we have $\Delta F \simeq\ 2.3\ {\rm mJy}$.
 Taking into account the $\nu^{-0.7}$ flux boost at lower
@@
 \begin{equation}\label{eq.delta_F_delta}
-    \Delta F(\delta) = \frac{\tcr{T_{\rm sys}A_{\rm eff}^{-1}}}{\cos(\delta-\phi_{\rm site})}
+    \Delta F(\delta) = \frac{T_{\rm sys}A_{\rm eff}^{-1}}{\cos(\delta-\phi_{\rm site})}
     {\sqrt{\frac{\cos\delta}{n_{\rm pol}\Delta\nu\Delta t(\delta=0)}}},

### 2017-03-15 ms_21cm.tex
foundation info

@@
 \begin{acknowledgements}
+This work was supported by the National Science Foundation of China (Grants No.
+11573006, 11528306), the Ministry of Science and Technology National Basic Science program (project 973) under grant No.
+2012CB821804.
 HRY acknowledges General Financial Grant No.2015M570884 and
